TSVD_MSSA

### 2025-03-24 Code/R/Research/TSVD_MSSA.Rmd
Final tsvd comparisons

## 0
A <- ones %o% rep(30, 5)
w <- rep(1 / 12, 5)
phi <- ones %o% rep(0, 5)
save_file_name <- "same_all"
groups_mssa <- list(1:2)
groups3 <- list(1)
groups_tsvd <- list(1:2)

@@

## 3
# A <- ones %o% rep(c(30, 28, 26, 24, 22), 2)[1:9]
# w <- rep(1 / 12, 9)
# phi <- ones %o% ((0:8) * 2 * pi / 3)
# save_file_name <- "same_freq_diff_phase"
# groups_mssa <- list(1:2)
# groups3 <- list(1:2)
# groups_tsvd <- list(1:4)

## 4
# A <- 20 * exp(ones %o% c(-rep(0.05, 9)) * 1:N)
# w <- rep(1 / 12, 9)
# phi <- ones %o% rep(0, 9)
# save_file_name <- "same_exp_same_freq"
# groups_mssa <- list(1:2)
# groups3 <- list(1)
# groups_tsvd <- list(1:2)

# 5
# A <- 20 * exp(ones %o% c(rep(0.05, 7), 0.03, 0.03) * 1:N)
# w <- rep(1 / 12, 9)
# phi <- ones %o% rep(0, 9)
# save_file_name <- "diff_exp_same_freq"
# groups_mssa <- list(1:4)
# groups3 <- list(1:2)
# groups_tsvd <- list(1:4)

## 6
# A <- 25 * exp(ones %o% c(-rep(0.05, 7), -0.03, -0.03) * 1:N)
# w <- rep(1 / 12, 9)
# phi <- ones %o% rep(0, 9)
# save_file_name <- "noise_mixing"
# groups_mssa <- list(1:2)
# groups3 <- list(1)
# groups_tsvd <- list(1:2)

>>>>

## 0
# A <- ones %o% rep(30, 5)
# w <- rep(1 / 12, 5)
# phi <- ones %o% rep(0, 5)
# save_file_name <- "same_all"
# groups_mssa <- list(1:2)
# groups3 <- list(1)
# groups_tsvd <- list(1:2)

@@

## 3
# A <- ones %o% rep(c(30, 28, 26, 24, 22), 2)[1:9]
# w <- rep(1 / 12, 9)
# phi <- ones %o% ((0:8) * 2 * pi / 3)
# save_file_name <- "same_freq_diff_phase"
# groups_mssa <- list(1:2)
# groups3 <- list(1:2)
# groups_tsvd <- list(1:3)

## 4
# A <- 20 * exp(ones %o% c(rep(0.05, 9)) * 1:N)
# w <- rep(1 / 12, 9)
# phi <- ones %o% rep(0, 9)
# save_file_name <- "same_exp_same_freq"
# groups_mssa <- list(1:2)
# groups3 <- list(1)
# groups_tsvd <- list(1:2)

## 5
# A <- 20 * exp(ones %o% c(rep(0.05, 7), 0.03, 0.03) * 1:N)
# w <- rep(1 / 12, 9)
# phi <- ones %o% rep(0, 9)
# save_file_name <- "diff_exp_same_freq"
# groups_mssa <- list(1:4)
# groups3 <- list(1:2)
# groups_tsvd <- list(1:2)

## 6
A <- 25 * exp(ones %o% c(-rep(0.05, 7), -0.03, -0.03) * 1:N)
w <- rep(1 / 12, 9)
phi <- ones %o% rep(0, 9)
save_file_name <- "noise_mixing"
groups_mssa <- list(1:2)
groups3 <- list(1)
groups_tsvd <- list(1:2)
